Git Learning Notes

### 2014-08-22 BackMatter/paper.tex
ch2 enhanced

\section{misc}
nucleation and film growth \cite{Hanbucken1984}

@@

\section{vocabulary}

adjunct to muscle power, computing and reasoning power, zinc-blende similarity, switching time depends on the velocity of the carriers; impact ionization, high field lead to nonlinear behavior, which arise from the major changes in the shape of the carrier distribution function, a far from equilibrium state.\footnote{\url{http://ieeexplore.ieee.org/xpl/tocresult.jsp?isnumber=31617&punumber=16}}

high field 600kV/cm. carrier, linear transport, constant relaxation time, mean free path longer than interatomic distances. the periodic potential does not cause scattering of the electrons. box normalization, wave vector is not a continuous variable. in ground state, topmost filled level is the Fermi level, crystal momentum, $hk$, or Fermi vector $k_F$ depends on the electron density. curvature mass, DOS mass in a state countering process,

Heat capacity is dominated by the electrons lying near the Fermi level. quantum effect and the coherence length ( 100nm at RT).

strike the wafer, sputter etching and plasma etching. fenestration, arrangement of windows and doors. sustained research,

experience an enormous development, principles underlying, scarce. heavily engaged, extensively used, become aware of, a great deal of, consistently used, lift the restriction, changed profoundly, denominator, a situation which often arises as ... in a manner similar to its counterpart.

in reciprocal space, primitive cell, a sketch of device, a decisive role. anchors,angular brackets, thermodynamical average over the equilibrium configuration at temperature T.

equation embodies the law of conservation, excess, set in consequentially.

become varied, laptop not hammer it hand, bubble pop, crash and burns. exert a marked influence, detrimental impact.

theoretical interest, phase transition, water droplets, water vapor cools, supersaturates and nucleates. aerosol, sulfuric acid, subsaturated, corrosion. union, cross, T. moisture,

profound effect, multiphonon bands, rich spectrum, Raman-active modes, atomic displacement giving rise to these modes, weaker restoring force in the vibrations. Interlayer van der Waals interaction, hydrocarbon contamination, an enlarged view of the boxed area, overlaid, ball-and-stick model fashion, a schematic view along [001]. Beam stop, in-plane stiffness, $\delta\omega/\epsilon$

>>>>

\section{misc}

E-beam spatial coherence.\cite{Morishita2013} phase contrast transfer function, coherence estimated by the visibility of double slits interference fringes, an effective diameter in specimen plane.  Image is a result of convolution between object and lens, point source on the focal plane, after lens the EM wavefront intersect image plane at different angle $\theta = d/f$,

nucleation and film growth \cite{Hanbucken1984}

@@

\section{vocabulary}
$\delta\omega/\epsilon$

### 2014-08-22 ch-intro/ch-instr.tex
ch2 enhanced

The SEM instrument used in this study is JEOL JSM-6480. The electron beam (E-beam) source is a tungsten filament heated at about 2800 K. The acceleration voltage can be up to 30 kV. After acceleration, electron beam strikes the sample mounted on specimen stage, producing rich signals as illustrated in Fig.~\ref{fig:ch2sem}. Depending on the energy and scattering angle, the out-coming electrons from specimen can be grouped as backscattering electron (BSE) and secondary electron (SE), respectively. SE is generated from the emission of valence band electrons. And due to the limited energy ($<50$ eV), the emission from deep region is mostly absorbed again; only those SE that are at the vicinity of specimen surface can escape. Hence the SE image is topographical sensitive. The emission efficiency is strongly affected by the geometry (tilting angle of specimen surface) and voltage potential (charging effect), so does the contrast in SE image. On the other hand, backscattered electron has large energy close to that of incident E-beam. The scattering efficiency strongly depends on atomic number (Z), thus allowing for the compositional analysis. The X-ray emission stems from inner shell transition of the constitutive atoms, and cathodoluminescence from bandgap transition. Other E-beam generated signals, such as Auger electrons, are not shown here.

@@

Crystal structures of the as-synthesized specimens in this study were characterized using PANXpert X’pert Pro MRD with Cu $K\alpha_{avg}$ radiation at $\lambda$=1.5418 \AA. The high energy photon ($E = 1239.8/0.15148= 8184.5$ eV) was generated using accelerated electron beam from tungsten filament to bombard Cu target. The $\theta-2\theta$ configuration was primarily used, as shown in Fig.~\ref{fig:ch2theta}. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{xrd_2theta.png}

@@

The nanostructures usually grew with preferred orientation; therefore, they cannot be treated as powders. The interpretation of XRD patterns could become difficult somehow. Two possible approaches could be followed to resolve this problem: one is using grazing angle XRD which could reveal in-plane domain size and orientation;\cite{Tersigni2011,Goorsky2002} the other is combining XRD with alternative techniques, such as Raman, TEM. The latter approach was taken in this work.

@@

TEM qualifies as a powerful and versatile tool for material characterization. JEOL JEM-2100 TEM with a \ce{LaB6} filament operated at 200 kV was used in current thesis. Similar to the photon-lattice interaction in XRD, the process of TEM could be understood as electron scattering events by the same crystal plane. In both processes, the constructive interference is described by $2d\sin\theta = \lambda$, where $d$ is crystal plane distance, $\lambda$ is incident wavelength (photon or electron), and $\theta$ is half of the scattering angle. A numerical comparison in Table.~\ref{tab:ch2tem} demonstrates the origin of difference in these two techniques.

@@

This small deviation angle determines the design of TEM column. In analog to the diffraction-limited resolution in conventional lens optics, the ultimate resolved point distance in TEM at 200 kV could be as small as 0.025 \AA. However it is much harder to manipulate electron with magnetic field than photon with dielectric lens, the current resolution in TEM is on the order of 1.0 \AA without correcting the spherical aberration. The nominal resolution of JEM-2100 is 2.3 \AA. On the other hand, it is much easier to fine tune the power (focal length) of lens in TEM than in conventional optics. This capacity enables other observation approaches that would be rather difficult, if not impossible, to be realized in lens optics, such as selected area electron diffraction pattern (SAED).

Akin to the electron-materials interaction introduced in Sec.~\ref{sec:sem}, X-ray emission and CL also occur in TEM, and these signals could be collected to obtain value insight into specimen at higher spatial resolution. In this study, the TEM specimen was prepared either by directly scratching the as-synthesized sample using TEM grid (Cu, lacy carbon, 300 mesh), or dispersed into aqueous or organic solutions, then drop-cast onto TEM grid. A JEOL double tilt holder was used to rotate the crystal orientation. TEM images and SEADs were acquired using a charge coupled device (CCD) from Gatan, inc. EDX spectroscopy was captured by similar Oxford Instrument INCA attachment.

The cost of TEM adds up to \$10 per eV. seize the public's imaginations. One must be just as aware of the instrument's limitations as one is of its advantages. Fundamental physics of electrons, how it is controlled by magnetic fields, how it interacts with specimen. TEM is essentially a signal-generating and detecting tool. TEM is initially developed to overcome the image resolution imposed by light microscopes. constitute, draw analogies, resolving power, correction of spherical aberration ($C_s$) and chromatic aberration ($C_c$), $C_s$ is done by , $C_c$ by energy-filtering, which is more useful for thicker specimens. E-beam is one type of ionizing radiation, which is capable of removing the tightly bound, inner-shell electrons from attractive field of nucleus (visible light, is non-ionizing radiation to some extent). a wide range of secondary signal can be produced, the spectra exhibits characteristic peaks, which identify the elements present in the specimen. In analog to laser as a highly coherent source, . The diameter of e-beam in TEM is less than 5nm in general, and can be $< 0.1$ nm at best. $C_s$ correction permits the generation of smaller electron probes with higher currents, which significantly improves both analytical spatial resolution and sensitivity. $C_c$ correction offer the possibility to form band-gap imaging and chemical-bond imaging. The limiting apertures increase the depth of field for specimen, and the depth of focus for the image. And the specimen is usually in focus from top to bottom surface.\cite{Williams2009}

Point-group and space-group determination from convergent-beam patterns. crystal symmetry analysis. e-beam wavelength in metal. The high-resolution comes at the cost of poor sampling. The limitations of TEM include small sampling, interpreting of the image. Human eyes and brain understand reflected light image, and not well-trained for the transmission images. The images, DPs and spectra are all averaged through the thickness of specimen. In other words, single TEM image has no depth sensitivity.

Both wave and particle approach, Electron scattering dictated by Coulomb interaction, Four aspects, the cross section (scattering probability), differential cross section (scattering angle), mean free path, and inelastic or elastic, non-scattering is invisible, backscattered in large angle and secondary electrons are of interest in SEM, where they provide Z contrast and surface-sensitive, topographical images. forward scattered is of interest in TEM. The spatial distribution of scattering is observed as contrast in images, and angular distribution is viewed in form of diffraction patterns. scattering events as billiard balls colliding, coherently scattered are those that remain in step, and incoherently scattered electrons have random phase relationship. Assuming single scattering events in TEM,

angle in radians, solid angle in steradians, cross section $\sigma$ in \si{m^2}, which when divided by area of atom, represents a probability that scattering event will occur. differential cross section for an isolated atom is $\frac{d\sigma}{d\Omega} = \frac{1}{2\pi \sin\theta} \frac{d\sigma}{d\theta}$. The total cross section is just $\sigma$ times atom number in unit volume. The mean free path is the inverse of $\sigma_{total}$, that is $\lambda_{MFP} = 1/\sigma_{total}$. penetrate electron cloud, spherical wavelets, the cross section for electrons elastically scattered into angles larger than $\theta$ is $\sigma_{nucleus}= 1.62\times10^{-24} (\frac{Z}{E_0})^2\cot^2\frac{\theta}{2}$; scattering factor $f(\theta)$ for low angle ($< \sim 3^{\circ}$). The positions of diffracted e-beams determined by size and shape of unit cell, and intensities governed by distribution, number, and types of atoms in the specimen.

@@

\begin{itemize}
\item X-ray: characteristic X-ray for elemental analysis, Bremsstrahlung X-ray also useful for biological sample; $K_\alpha$ line from L to K transition, and $K_\beta$ from M to K transition, $L_\alpha$ line from M to L transition, Inelastic cross section, Bethe expression, X-ray energies are not identical to the ionized energy because after first emission, the atom is not in ground state until a free electron fill the last hole in the outermost shell. A cascade of transitions, Coster-Kroning transition, X-ray line shift slightly due to the chemical bonding to another atom. XEDS is not good at analyzing light elements due to the low fluorescence yield, which is strongly dependent on Z. Bremsstrahlung X-ray emission is strongly forward, 
\item SE: ejected from the conduction or valence bands, weak so only escaping if near the surface, STEM, complex cross section mechanism, 
\item Auger: Auger electron has specific energy similar to X-Ray, but is much more strongly absorbed than X-ray. Stated another way, Auger electron is hard to escape, so it is a surface sensitive. 
\item CL: spatial resolution around 100 nm, 
\item collective interaction, plasmon and phonon, plasmon excitation cross section in Lorenztian form $\frac{d\sigma_\theta}{d\Omega} = \frac{1}{2\pi a_0} \frac{\theta_E}{\theta^2 + \theta_E^2}$, where $\theta_E = E_p/2E_0$, 
\end{itemize}

@@

detrimental, available means, safety as a primary concern, radiation-leak test, used in isolation, telepresence, increasingly attractive feature, give rise to, worth illustrating, remain unaffected, stated another way, line of thought, reduced and lowered, electron crystallography, interplanar spacing, intrinsic to the specimen,

\section{Raman and UV-Vis Spectroscopy}

\url{http://www.kayelaby.npl.co.uk/chemistry/3_8/3_8_5.html}

Raman spectroscopy, a common vibrational spectroscopy, is based on the inelastic scattering of a monochromatic excitation source in energy range of 100 to 4000 \si{cm^{-1}}. Being nondestructive and requiring minimal preparation, 
it is an excellent tools to assess lattice dynamics and fingerprint species.\cite{McCreery2000}

@@

A Raman pattern database can be found at \url{http://wwwobs.univ-bpclermont.fr/sfmc/ramandb2/index.html}.

@@

\section{Substrates and Pre-growth Treatments}\label{ch2sub}

@@

Image J.\cite{Schneider2012} TEM lattice measurement.

Fityk. \cite{Wojdyr2010}

XRD pattern, Spectra(EDX, Raman, UV-Vis) redraw using Origin Pro 8.0.

>>>>

The SEM instrument used in this study is JEOL JSM-6480. The electron beam (E-beam) source is a tungsten filament heated at about 2800 K. The acceleration voltage can be up to 30 kV. After acceleration, electron beam strikes the sample mounted on specimen stage, producing rich signals as illustrated in Fig.~\ref{fig:ch2sem}. Depending on the energy and scattering angle, the out-coming electrons from specimen can be grouped into backscattering electron (BSE) and secondary electron (SE), respectively. SE is generated from the emission of valence band electrons. And due to the limited energy ($<50$ eV), the emission from deep region is mostly absorbed again; only those SE that are at the vicinity of specimen surface can escape. Hence the SE image is topographical sensitive. The emission efficiency is strongly affected by the geometry (tilting angle of specimen surface) and voltage potential (charging effect), so does the contrast in SE image. On the other hand, backscattered electron could have large energy close to that of incident E-beam. The scattering cross section strongly depends on atomic number (Z), thus allowing for the compositional analysis. The X-ray emission stems from inner shell transition of the constitutive atoms, and cathodoluminescence from bandgap transition. Other E-beam generated signals, such as Auger electrons, are not useful unless with ultra-high vacuum and clean surface.

@@

Crystal structures of the as-synthesized specimens in this study were characterized using PANXpert Pro MRD with Cu $K\alpha_{avg}$ radiation at $\lambda$=1.5418 \AA. The high energy photon ($E = 1239.8/0.15148= 8184.5$ eV) was generated using accelerated electron beam from tungsten filament to bombard Cu target. The $\theta-2\theta$ configuration was primarily used, as shown in Fig.~\ref{fig:ch2theta}. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{xrd_2theta.png}

@@

The nanostructures usually grew with preferred orientation; therefore, they cannot be treated as powders. The interpretation of XRD patterns could become difficult somehow. Two possible approaches could be followed to resolve this problem: one is using grazing angle XRD which could reveal in-plane domain size and orientation;\cite{Tersigni2011,Goorsky2002} the other is combining XRD with alternative techniques, such as Raman, TEM. The latter approach was pursued in this work.

@@

TEM qualifies as a very powerful and versatile tool for material characterization. Akin to the electron-materials interaction introduced in Sec.~\ref{sec:sem}, various signals are generated when the thin specimen was radiated by electron beam. Besides the SAED pattern and HRTEM imaging, other TEM based techniques include CBED, EDX, EELS and CL, etc. Therefore, TEM is essentially a signal-generating and detecting tool. Fundamental physics of electron is needed to obtain a comprehensive understanding of these TEM related techniques. Only a brief summary is given here.

Electron scattering was dictated by Coulomb interaction, and can be characterized by the following four aspects: the cross section (scattering probability), differential cross section (scattering angle), mean free path, and inelastic or elastic scattering. The cross section $\sigma$ in \si{m^2}, which when divided by area of targeting atom, represents a probability that scattering event will occur. Differential cross section for an isolated atom is 
\[
\frac{d\sigma}{d\Omega} = \frac{1}{2\pi \sin\theta} \frac{d\sigma}{d\theta},
\] 
where $\theta$ is scattering angle in radians, $\Omega$ is solid angle in steradians (sr), and $\theta$ is half of the scattering angle. The total cross section is just $\sigma$ times atom numbers in unit volume. The mean free path is the inverse of $\sigma_{total}$, that is $\lambda_{MFP} = 1/\sigma_{total}$.

The spatial distribution of scattering is observed as contrast in images, and angular distribution is viewed in form of diffraction patterns. The positions of diffracted E-beams are determined by size and shape of unit cell, and intensities governed by distribution, number, and types of atoms in the specimen.

JEOL JEM-2100 TEM with a \ce{LaB6} filament operated at 200 kV was used in current thesis. A numerical comparison between the scattering events in XRD and TEM is provided to visualize the difference. In both processes, the constructive interference is described by $2d\sin\theta = \lambda$, where $d$ is crystal plane distance, $\lambda$ is incident wavelength (photon or electron), and $\theta$, again, is half of the scattering angle. Table.~\ref{tab:ch2tem} demonstrates the origin of difference in these two techniques.

@@

This small deviation angle determines the way of secondary signal usage in TEM. In analog to the diffraction-limited resolution in conventional lens optics, the ultimate resolved point distance in TEM should be on the order of electron wavelength used, which is 0.025 \AA at 200 kV. However, it is generally more difficult to manipulate electron with magnetic field than do photon with dielectric lens. The current resolving power in TEM is on the order of 1.0 \AA without correction of spherical aberration. The nominal resolution of JEM-2100 is 2.3 \AA. On the other hand, it is much easier to fine tune the power (focal length) of lens in TEM than in conventional optics. This capacity enables other observation approaches that would be rather difficult, if not impossible, to be realized in lens optics, such as selected area electron diffraction pattern (SAED).

In this study, the TEM specimen was prepared either by directly scratching the as-synthesized sample using TEM grid (Cu, lacy carbon, 300 mesh), or dispersed into aqueous or organic solutions, then drop-cast onto TEM grid. A JEOL double tilt holder was used to rotate the crystal orientation. TEM images and SEADs were acquired using a charge coupled device (CCD) from Gatan, inc. EDX spectroscopy was captured by similar Oxford Instrument INCA attachment.

To make the best out of TEM analysis, one also needs to be aware of the limitations of TEM. Two aspects were pointed out here, including small sampling and interpreting of the image. The former one is inherent and can only be partially overcome by combining TEM with other ensemble characterization tools. As to the latter one, it should be noted that the specimen is usually in focus from top to bottom surface; therefore the images, DPs and spectra are all averaged through the thickness of specimen. In other words, single TEM image has no depth sensitivity.\cite{Williams2009}

\iffalse
Similar to the photon-lattice interaction in XRD, the process of TEM could be understood as electron scattering events by the same crystal plane.

\begin{itemize}
\item X-ray: characteristic X-ray for elemental analysis, Bremsstrahlung X-ray also useful for biological sample; $K_\alpha$ line from L to K transition, and $K_\beta$ from M to K transition, $L_\alpha$ line from M to L transition, Inelastic cross section, Bethe expression, X-ray energies are not identical to the ionized energy because after first emission, the atom is not in ground state until a free electron fill the last hole in the outermost shell. A cascade of transitions, Coster-Kroning transition, X-ray line shift slightly due to the chemical bonding to another atom. XEDS is not good at analyzing light elements due to the low fluorescence yield, which is strongly dependent on Z. Bremsstrahlung X-ray emission is strongly forward, 
\item SE: ejected from the conduction or valence bands, weak so only escaping if near the surface, STEM, complex cross section mechanism, 
\item Auger: Auger electron has specific energy similar to X-Ray, but is much more strongly absorbed than X-ray. Stated another way, Auger electron is hard to escape, so it is surface sensitive. 
\item CL: spatial resolution around 100 nm, 
\item collective interaction, plasmon and phonon, plasmon excitation cross section in Lorenztian form $\frac{d\sigma_\theta}{d\Omega} = \frac{1}{2\pi a_0} \frac{\theta_E}{\theta^2 + \theta_E^2}$, where $\theta_E = E_p/2E_0$, 
\end{itemize}

The diameter of E-beam in TEM is less than 5 nm in general, and can be $< 0.1$ nm at best.

correction of spherical aberration ($C_s$) and chromatic aberration ($C_c$), $C_s$ is done by , $C_c$ by energy-filtering, which is more useful for thicker specimens. $C_s$ correction permits the generation of smaller electron probes with higher currents, which significantly improves both analytical spatial resolution and sensitivity. $C_c$ correction offer the possibility to form band-gap imaging and chemical-bond imaging. The limiting apertures increase the depth of field for specimen, and the depth of focus for the image.\cite{Williams2009}

including controlling the interactions of electron with magnetic fields and with specimen.

@@

penetrate electron cloud, spherical wavelets, the cross section for electrons elastically scattered into angles larger than $\theta$ is $\sigma_{nucleus}= 1.62\times10^{-24} (\frac{Z}{E_0})^2\cot^2\frac{\theta}{2}$; scattering factor $f(\theta)$ for low angle ($< \sim 3^{\circ}$).

Point-group and space-group determination from convergent-beam patterns. crystal symmetry analysis. e-beam wavelength in metal. The high-resolution comes at the cost of poor sampling.  Human eyes and brain understand reflected light image, and not well-trained for the transmission images.

One must be just as aware of the instrument's limitations as one is of its advantages.   TEM is initially developed to overcome the image resolution imposed by light microscopes. constitute, draw analogies, resolving power, E-beam is one type of ionizing radiation, which is capable of removing the tightly bound, inner-shell electrons from attractive field of nucleus (visible light, is non-ionizing radiation to some extent). a wide range of secondary signal can be produced, the spectra exhibits characteristic peaks, which identify the elements present in the specimen. In analog to laser as a highly coherent source, .

Both wave and particle approach, non-scattering is invisible, backscattered in large angle and secondary electrons are of interest in SEM, where they provide Z contrast and surface-sensitive, topographical images. forward scattered is of interest in TEM.  scattering events as billiard balls colliding, coherently scattered are those that remain in step, and incoherently scattered electrons have random phase relationship. Assuming single scattering events in TEM,

The cost of TEM adds up to \$10 per eV. seize the public's imaginations.

@@

\fi
\section{Raman and UV-Vis Spectroscopy}

Raman spectroscopy, a common vibrational spectroscopy, is based on the inelastic scattering of a monochromatic excitation source with photon energy variation range of 100 to 4000 \si{cm^{-1}}. This energy difference between incident photon and inelastically scattered photon is closely related to a series of vibrational modes. Being nondestructive and requiring minimal preparation, it is an excellent tools to assess lattice dynamics and fingerprint species.\cite{McCreery2000} For instances, characteristic Raman shift can be used to determine material compositions; changes in Raman peak (FWHM, frequency shift) are often related to strain; polarization Raman spectra can be used to derive crystal orientation and symmetry.

@@

\iffalse
A Raman pattern database can be found at \url{http://wwwobs.univ-bpclermont.fr/sfmc/ramandb2/index.html}.

In analytical practice, frequency is expressed in reciprocal wavelength (as cm−1), called wavenumbers;

@@

\iffalse

hemispherical reflectance, 
diffusive reflectance is a mathematical artifice without direct physical meaning.

p332- 338

\fi
\section{Substrates and Pre-growth Treatments}\label{ch2sub}

@@

The SEM images are cropped using Adobe Photoshop for highlighting the features and fitting into text width. To obtain the dimension of specimen, scale bar was measured and compared to the size of interest using ImageJ\cite{Schneider2012} for SEM, TEM images and SAED pattern. It is worth noting that ImageJ could directly read the dm3 format generated in Gatan imaging software, which is more productive than the scale bar method.

Various spectra, be it from XRD, EDX, Raman, or UV-Vis, were redraw using Origin Pro 8.0. The peak fitting was performed using Fityk, a nonlinear curve fitting program specialized in data processing from powder diffraction, chromatography, photoluminescence and photoelectron spectroscopy, infrared and Raman spectroscopy, \emph{etc}.\cite{Wojdyr2010}

\iffalse
incoherent illumination $s = \frac{1.22 \lambda_{vac}}{2n\sin i}$, 
coherent illumination in microscope $s = \frac{\lambda_{vac}}{n\sin i}$,, 
phase contrast: transforming phase change in object plane into amplitude variation in image plane. 
much better than needed, human eye resolving power 0.3 mrad,

The illumination can be considered as incoherent (adding intensity) if the object is self-luminous, or if illminated from all direction.

The opposite occurs in TEM probably, where the specimen is irradiated with complete transverse coherence across its area. back 
focal plane displays the Fourier transform of complex amplitude in object plane. The optical system is a spatial low-pass filter: it builds up images from only the low Fourier components present at the object, having higher values cutoff.

with the aid of Fig.
